%-------------------------
% Resume in Latex
% Author : Jake Gutierrez
% Based off of: https://github.com/sb2nov/resume
% License : MIT
%------------------------

\documentclass[letterpaper,11pt]{article}

\usepackage{latexsym}
\usepackage[empty]{fullpage}
\usepackage{titlesec}
\usepackage{marvosym}
\usepackage[usenames,dvipsnames]{color}
\usepackage{verbatim}
\usepackage{enumitem}
% \usepackage{xcolor}
\usepackage[colorlinks=true, linkcolor=blue, urlcolor=blue, citecolor=blue]{hyperref}
% \definecolor{darkblue}{RGB}{0, 0, 139} % Darker than standard blue
\usepackage{fancyhdr}
\usepackage[english]{babel}
\usepackage{tabularx}
\usepackage{fontspec}
\defaultfontfeatures{Ligatures=TeX}


%----------FONT OPTIONS----------
% sans-serif
% \usepackage[sfdefault]{FiraSans}
% \usepackage[sfdefault]{roboto}
% \usepackage[sfdefault]{noto-sans}
% \usepackage[default]{sourcesanspro}

% serif
% \usepackage{CormorantGaramond}
% \usepackage{charter}


\pagestyle{fancy}
\fancyhf{} % clear all header and footer fields
\fancyfoot{}
\renewcommand{\headrulewidth}{0pt}
\renewcommand{\footrulewidth}{0pt}

% Adjust margins
\addtolength{\oddsidemargin}{-0.5in}
\addtolength{\evensidemargin}{-0.5in}
\addtolength{\textwidth}{1in}
\addtolength{\topmargin}{-.5in}
\addtolength{\textheight}{1.0in}

\urlstyle{same}

\raggedbottom
\raggedright
\setlength{\tabcolsep}{0in}

% Sections formatting
\titleformat{\section}{
  \vspace{-4pt}\scshape\raggedright\large
}{}{0em}{}[\color{black}\titlerule \vspace{-5pt}]

%-------------------------
% Custom commands
\newcommand{\resumeItem}[1]{
  \item\small{
    {#1 \vspace{-2pt}}
  }
}

\newcommand{\resumeSubheading}[4]{
  \vspace{-2pt}\item
    \begin{tabular*}{0.97\textwidth}[t]{l@{\extracolsep{\fill}}r}
      \textbf{#1} & #2 \\
      \textit{\small#3} & \textit{\small #4} \\
    \end{tabular*}\vspace{-7pt}
}

\newcommand{\resumeSubheadingDouble}[6]{
  \vspace{-2pt}\item
    \begin{tabular*}{0.97\textwidth}[t]{l@{\extracolsep{\fill}}r}
      \textbf{#1} & #2 \\
      \textit{\small#3} & \textit{\small #4} \\
      \textit{\small#5} & \textit{\small #6} \\
    \end{tabular*}\vspace{-7pt}
}

\newcommand{\resumeSubSubheading}[2]{
    \item
    \begin{tabular*}{0.97\textwidth}{l@{\extracolsep{\fill}}r}
      \textit{\small#1} & \textit{\small #2} \\
    \end{tabular*}\vspace{-7pt}
}

\newcommand{\resumeProjectHeading}[3]{
\vspace{-2pt}\item
    \begin{tabular*}{0.97\textwidth}{l@{\extracolsep{\fill}}r}
      \textbf{#1} & #2 \\
      \textit{\small#3} & \space \\
    \end{tabular*}\vspace{-7pt}
}

\newcommand{\resumeSubItem}[1]{\resumeItem{#1}\vspace{-4pt}}

\renewcommand\labelitemii{$\vcenter{\hbox{\tiny$\bullet$}}$}

\newcommand{\resumeSubHeadingListStart}{\begin{itemize}[leftmargin=0.15in, label={}]}
\newcommand{\resumeSubHeadingListEnd}{\end{itemize}}
\newcommand{\resumeProjectListStart}{\begin{itemize}[leftmargin=0.15in, label={}]}
\newcommand{\resumeProjectListEnd}{\end{itemize}}
\newcommand{\resumeItemListStart}{\begin{itemize}}
\newcommand{\resumeItemListEnd}{\end{itemize}\vspace{-5pt}}

%-------------------------------------------
%%%%%%  RESUME STARTS HERE  %%%%%%%%%%%%%%%%%%%%%%%%%%%%


\begin{document}

\begin{center}
    \textbf{\Huge \scshape Dion Osmani}
\end{center}


%-----------EDUCATION-----------
\section{Education}
  \resumeSubHeadingListStart
    \resumeSubheading
      {HES-SO, School of Engineering}{Sion, VS}
      {BSc Computer Science and Communication Systems, Data Engineering}{August 2022 -- Sept. 2025}
    \resumeSubheadingDouble
      {Technical and Vocational School}{Sion, VS}
      {Federal VET Diploma in IT, Systems and Networks, \href{https://drive.google.com/file/d/1WFuTH7d8QYcOMaClUea2DzW2HeszU424/view?usp=sharing}{view certificate}}{Aug. 2018 -- June 2022}
      {Technical Matura, \href{https://drive.google.com/file/d/1-RyMzu1c0irF1EqTaxk4OTzXyMbAzzgg/view?usp=drive_link}{view certificate}}{"}
  \resumeSubHeadingListEnd


%-----------Experience-----------
\section{Experience}
  \resumeSubHeadingListStart

    \resumeSubheading
      {HES-SO, School of Engineering - Informatics Institute (SIMLab)}{September 2025 --}
      {Research Assistant}{Sion, VS}
      \resumeItemListStart
      \resumeItem{Contributing to research in scientific and industrial machine learning, focusing on hybrid modeling, and explainable AI in collaboration with academic and industry partners.}
      \resumeItem{Assisting in diverse classes, including \textit{Introduction to Programming} and \textit{Computational Physics}, supporting instruction and student learning.}
      \resumeItemListEnd

    \resumeSubheading
    {HES-SO, Infrastructure Competency Center}{August 2021 -- July 2022}
    {Intern, \href{https://drive.google.com/file/d/1JspdtGHWfH57NsNkazgo6VZaCslR6hu4/view?usp=sharing}{view certificate}}{Sion/Sierre, VS}
    \resumeItemListStart
    \resumeItem{Designed and developed an automatic naming and categorization system for virtual machines in a vSphere environment.}
    \resumeItem{Developed a progressive web application to facilitate the creation of virtual machines by business users, thereby reducing the workload of system administrators.}
    \resumeItemListEnd

  \resumeSubHeadingListEnd



%-----------Extracurriculars-----------
\section{Extracurricular Activities}
  \resumeSubHeadingListStart

  \resumeSubheading
    {Career Promotion}{August 2022 --}
    {Facilitator}{VS}
    \resumeItemListStart
        \resumeItem{Presented educational opportunities that provide access to university-level education, explaining possible career paths to young people.}
        \resumeItem{Raised awareness among students about artificial intelligence, presenting the current state of the field and its practical applications.}
    \resumeItemListEnd

  \resumeSubHeadingListEnd

% -----------Skill and Interests-----------
% \section{Skills \& Interests}
%  \begin{itemize}[leftmargin=0.15in, label={}]
%     \small{\item{
%     \vspace{1mm}
%      \textbf{Skills}{: } \\
%      \vspace{1mm}
%      \textbf{Interests}{: Photography, Creative Writing, Archery, New York Knicks} \\
%      \vspace{1mm}

%     }}
%  \end{itemize}

% Projects
\section{Projects}
\resumeProjectListStart

\resumeProjectHeading
    {PETAL}{\href{https://github.com/dij0s/PETAL}{github.com/dij0s/PETAL}}
    {Academic Project - BSc thesis}
    \resumeItemListStart
    \resumeItem{Designed and implemented a modular multi-agent AI architecture for municipal energy planning, orchestrating specialized agents using LangGraph.}
    \resumeItem{Engineered a scalable, fully open-source architecture using containerization and modular design principles, enabling seamless integration of conversational AI, real-time data storage, and interactive web interfaces.}
    \resumeItem{Prioritized user experience by implementing a conversational interface with adaptive preference memory and interactive geospatial visualization, supporting actionable, guideline-compliant recommendations for Swiss municipalities.}
    \resumeItem{Developed a robust evaluation framework combining domain expert assessment and automated LLM-as-a-judge benchmarking (G-eval), demonstrating statistically significant improvements in contextual reasoning and structured planning with larger language models.}
\resumeItemListEnd

\vspace{1mm}

\resumeProjectHeading
    {AMR}{\href{https://github.com/dij0s/AMR}{github.com/dij0s/AMR}}
    {Academic Project}
    \resumeItemListStart
        \resumeItem{Developed an Adaptive Mesh Refinement (AMR) algorithm in Python, optimizing computational resources with a $\sim95\%$ reduction in execution time.}
        \resumeItem{Implemented an efficient Quadtree/Octree data structure for numerical simulation, with a $\sim92\%$ reduction in memory usage.}
        \resumeItem{Solved heat diffusion equations using a second-order finite difference scheme, validated by comparison with a reference solution.}
    \resumeItemListEnd
\resumeProjectListEnd

\vspace{5mm}

\begin{center}
\small +41 78 742 1190 $|$
\href{mailto:dion.08osmani@gmail.com}{dion.08osmani@gmail.com} $|$
\href{https://www.linkedin.com/in/dion-osmani-60478720b/}{linkedin.com} $|$
\href{https://github.com/dij0s/}{github.com} $|$
\href{https://dionosmani.vercel.app}{dionosmani.vercel.app}
\end{center}

\end{document}
